### 2016-05-28 R/ITHIM.Rmd
Update to ITHIM.Rmd

```{r AF}
100*round(AF$BreastCancer[-(1:2),],4)

```{r explore}
names(ITHIM.baseline$parameters)
```

We use Rws to estimate mean walking speed and from that mean walking
METs.  Mean cycling METs, however, is constant and is not a function
of mean cycling speed or Rcs.  So, I do not think Rcs is currently
used.

@@

```{r plot1, echo = FALSE}
D <- melt(ITHIM$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

```{r plot2, echo = FALSE}
D <- melt(ITHIM$parameters$Rwt, c("age","sex"), value.name = "rhowt")
p <- ggplot(D, aes(age,  rhowt)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

>>>>

```{r AF, echo = FALSE}
lapply(AF[-(which(names(AF)%in%c("CVD","Diabetes")))], function(x) 100*round(x[-(1:2),],4))
```
### Relative Risk Model
```{r explore}
names(ITHIM.baseline$parameters)
```
```{r RRFigure, echo = FALSE}
phi <- function(x,k=0.5,phi0=RR$BreastCancer$F[1,1]) phi0^{x^k}
plot(x = xvec <- seq(0,xmax <- 10,length.out=1e3), y = phi(xvec, k = 0.25), main = "Relative Risk Models for MET Exposure", xlab = "METs per week", ylab = "Breast Cancer Relative Risk", type = "l", lwd = 2, col = 1, ylim = c(0.9,1),xlim=c(0,xmax))
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.375), lwd = 2, col = 3)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 0.5), lwd = 2, col = 2)
lines(x = xvec <- seq(0,xmax,length.out=1e3), y = phi(x = xvec, k = 1), lwd = 2, col = 4)
legend(x="topright",legend=paste0("k=",c("0.25","0.375","0.5","1")), col=1:4,lty=1,lwd=2)
```

@@

```{r plot1, echo = FALSE}
D <- melt(ITHIM.baseline$means$meanActiveTransportTime, c("age","sex"), value.name = "activeTransportTime")
p <- ggplot(D, aes(age,  activeTransportTime)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```

```{r plot2, echo = FALSE}
D <- melt(ITHIM.baseline$parameters$Rwt, c("age","sex"), value.name = "rhowt")
p <- ggplot(D, aes(age,  rhowt)) + geom_bar(aes(fill=sex), stat = "identity", position = "dodge")
p
```
